---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# glossary

<!-- badges: start -->
[![R-CMD-check](https://github.com/r-devel/glossary/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/r-devel/glossary/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of this package is to manage a glossary for R translation projects. The idea is based on [a proposal](https://github.com/SaranjeetKaur/isc_proposal_translations) created by [Saranjeet Kaur Bhogal (@SaranjeetKaur)](https://github.com/SaranjeetKaur/). The project was launched during the [R Dev Day @ RSE Con25](https://warwick.ac.uk/fac/sci/statistics/news/r-dev-day-rsecon25). This is repo is currently Work in Progress.

## Installation

You can install the development version of glossary from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("r-devel/glossary")
```

## With `Write` permissions:

Steps to add pre-commit:

1. Do the following in the Terminal application of your machine. Do not do this in RStudio Terminal:
    1. For windows `pip3 install pre-commit --user`
    2. For mac `brew install pre-commit` 
2. Clone the repo https://github.com/r-devel/glossary to a local folder.  
3. Go to RStudio Console and type 
```{r}
install.packages("devtools")
install.packages("precommit")
precommit::use_precommit()
```

This will open pre-commit interface in browser. Sign into it with GitHub.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(glossary)
## basic example code
```

## Contributors


<!-- ALL-CONTRIBUTORS-LIST:START - Do not remove or modify this section -->
<!-- prettier-ignore-start -->
<!-- markdownlint-disable -->

All contributions to this project are gratefully acknowledged using the [`allcontributors` package](https://github.com/ropensci/allcontributors) following the [all-contributors](https://allcontributors.org) specification. Contributions of any kind are welcome!

<table>

<tr>
<td align="center">
<a href="https://github.com/SaranjeetKaur">
<img src="https://avatars.githubusercontent.com/u/28556616?v=4" width="100px;" alt=""/>
</a><br>
<a href="https://github.com/r-devel/glossary/commits?author=SaranjeetKaur">SaranjeetKaur</a>
</td>
<td align="center">
<a href="https://github.com/rivaquiroga">
<img src="https://avatars.githubusercontent.com/u/31421616?v=4" width="100px;" alt=""/>
</a><br>
<a href="https://github.com/r-devel/glossary/commits?author=rivaquiroga">rivaquiroga</a>
</td>
</tr>

</table>

<!-- markdownlint-enable -->
<!-- prettier-ignore-end -->
<!-- ALL-CONTRIBUTORS-LIST:END -->
